Figures to insert in text

### 2018-03-08 Chapters/Chapter02.tex
sdm

Of course, there is also new work here.  The mathematics of the model has been to be correct (with a single exception); we have shown how to execute unsupervised learning with nothing besides operations originally proposed by Kanerva; and finally, we have reproduced

>>>>

Of course, there is also new work here.  The mathematics of the model has been shown to be correct (with a single exception); we have shown how to execute unsupervised learning with nothing besides operations originally proposed by Kanerva; we have studied the generalized Murilo read; we have seen and finally, we have reproduced
